Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
Better case distinction in lem:1req
Much better name for k=3 ALG

\newcommand{\OPT}{\mathit{OPT}}
\newcommand{\ALG}{ALG}
\newcommand{\OBRP}{BRP}
\newcommand{\PPOBRP}{PP-BRP}
\newcommand{\TAlg}{{\ensuremath{ALG_{k=3}}}\xspace} % we should change this name

@@

    Consider a request $(u, v)$ that triggered the repartitiong and let $U, V$ be clusters of these nodes.
    Note that $U\neq V$, as such a request cannot trigger a reconfiguration.
    We consider cases upon the type of clusters $U$ and $V$.
    Note that this is impossible that either $U$ or $V$ is of type $C_3$, as otherwise we encounter a component of size $4$ and this would contradict the case assumption that the component-respecting partition exists.
    If either $U$ or $V$ is of type $C_1$, then this cluster can fit the merged component, and the rebalance is local within $U$ and $V$, for the cost of at most $3$ migrations.

@@

\begin{theorem}
  \TAlg is $O(\ell)$-competitive.
\end{theorem}
\begin{proof}
  Fix a completed phase of \TAlg, and consider the state of its counters at the end of it.
  We consider the incomplete phase later in this proof.
  We say that the pair $(u, v)$ is \emph{saturated}, if the counter has value $\alpha$, and \emph{unsaturated} otherwise.

>>>>

\newcommand{\OPT}{\mathit{OPT}}
\newcommand{\ALG}{ALG}
\newcommand{\OBRP}{BRP}
\newcommand{\PPOBRP}{PP-BRP}
\newcommand{\TAlg}{{\ensuremath{\textsc{ALG}_{3}}}\xspace} % we should change this name

@@

    Consider a request $(u, v)$ that triggered the repartitiong and let $U, V$ be clusters of these nodes.
    Note that $U\neq V$, as such a request cannot trigger a reconfiguration.
    We consider cases upon types of clusters $U$ and $V$.
    Note that this is impossible that either $U$ or $V$ is of type $C_3$, as otherwise we encounter a component of size $4$ and this would contradict the case assumption that the component-respecting partition exists.
    If either $U$ or $V$ is of type $C_1$, then this cluster can fit the merged component, and the rebalance is local within $U$ and $V$, for the cost of at most $3$ migrations.

@@

\begin{theorem}
  \TAlg is $O(\ell)$-competitive.
\end{theorem}
\begin{proof}
  Fix a completed phase, and consider the state of \TAlg's counters at the end of it.
  We consider the incomplete phase later in this proof.
  We say that the pair $(u, v)$ is \emph{saturated}, if the counter has value $\alpha$, and \emph{unsaturated} otherwise.
